
%!TEX root = ../main.tex

\section{Conclusion}
%We presented a method for learning rules that may contain negated atoms from KGs that
%dynamically exploits feedback from a precomputed embedding model. 
%Our approach is general in that any embedding model can be utilized including text-enhanced ones, which indirectly allows us to 
%harness
%unstructured 
%web sources 
%for rule learning.
% We evaluated our approach with various configurations on real-world datasets and observed significant improvements
%over state-of-the-art rule learning systems.\looseness=-1
%
%An interesting future direction is to extend our work to more complex non-monotonic rules with higher-arity predicates,
%aggregates and existential variables or disjunctions in rule heads, which is challenging due to inevitable scalability issues.

Awareness of entities and types has greatly advanced semantic search
both for querying the web of linked data and for Internet search engines.
In contrast, coping with quantities in text content and in query constraints
has hardly received any attention, yet is an important case.
This paper has presented the Qsearch system for full-fledged support of
quantity queries, through new ways of information extraction and 
answer matching and ranking.
We capture quantities in their full extent, including units of measures,
reference entities and the relevant contexts.
The model for Qfacts and Qqueries is relatively simple but highly versatile and effective.
%a more detailed structured modeling would not be able to cope with the
%uncertainty in textual inputs and the approximate matching of candidate answers.
A key asset of Qsearch is its high quality in extracting Qfacts,
recognizing the right entity-quantity pairs even in complex sentences.

Future work includes devising additional ways of aggregating Qfacts with
the same candidate answer, so as to obtain strong signals from many
noisy cues (i.e., when the same entity-quantity pair occurs in many pages,
but mostly in the form of crude estimates or vague hints).
Also, we plan to extend the Qquery model to incorporate queries that
contain multiple quantity conditions (e.g., hybrid SUVs with range above 500 miles
and energy consumption above 40 MPGe).




